### 2022-01-01 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@712a8befa336a6cc3f43b1c5041e1deb3e9fe107 🚀

\textbf{Fig 1}: Recreation of the figure in \texttt{nlmpy} paper and the
source

\hypertarget{comparison-to-nlmpy-and-nlmr}{%
\section{\texorpdfstring{Comparison to \texttt{nlmpy} and
\texttt{NLMR}}{Comparison to nlmpy and NLMR}}\label{comparison-to-nlmpy-and-nlmr}}

@@

>>>>

This software can generate neutral landscapes using twenty different
methods.

fig.~\ref{fig:allmethods} shows a replica of Figure 1 from
(\textbf{nlmpycite?})

Table of methods.

\begin{figure}
\hypertarget{fig:allmethods}{%
\centering
\includegraphics{./figures/figure1.png}
\caption{Recreation of the figure in \texttt{nlmpy} paper and the
source}\label{fig:allmethods}
}
\end{figure}

\begin{verbatim}
using NeutralLandscapes, Plots
siz = 50, 50

Fig1a = rand(NoGradient(), siz) # Random NLM
Fig1b = rand(PlanarGradient(), siz) # Planar gradient NLM
Fig1c = rand(EdgeGradient(), siz) # Edge gradient NLM
Fig1d = falses(siz) 
Fig1d[10:25, 10:25] .= true # Mask example
Fig1e = rand(DistanceGradient(findall(vec(Fig1d))), siz) # Mask example
Fig1f = rand(MidpointDisplacement(0.75), siz) # Mask example
Fig1g = rand(RectangularCluster(4, 8), siz)
Fig1h = rand(NearestNeighborElement(200), siz)
Fig1i = rand(NearestNeighborCluster(0.4), siz)
Fig1j = blend([Fig1f, Fig1c])
Fig1k = blend(Fig1h, Fig1e, 1.5)
Fig1l = classify(Fig1i, ones(4))
Fig1m = classify(Fig1a, [1-0.5, 0.5])
Fig1n = classify(Fig1g, [1-0.75, 0.75])
Fig1o = classify(Fig1f, ones(3))
Fig1p = classify(Fig1f, ones(3), Fig1d)
Fig1q = rand(PlanarGradient(90), siz, mask = Fig1n .== 2) #TODO mask as keyword + should mask be matrix or vec or both? (Fig1e)
Fig1r = ifelse.(Fig1o .== 2, Fig1m .+ 2, Fig1o)
Fig1s = rotr90(Fig1l)
Fig1t = Fig1o'

class = cgrad(:Set3_4, 4, categorical = true)
c2, c3, c4 = class[1:2], class[1:3], class[1:4]

gr(color = :fire, ticks = false, framestyle = :box, dpi=500, colorbar = false)
plot(
    heatmap(Fig1a),         heatmap(Fig1b),         heatmap(Fig1c),         heatmap(Fig1d, c = c2), heatmap(Fig1e),
    heatmap(Fig1f),         heatmap(Fig1g),         heatmap(Fig1h),         heatmap(Fig1i),         heatmap(Fig1j), 
    heatmap(Fig1k),         heatmap(Fig1l, c = c4), heatmap(Fig1m, c = c2), heatmap(Fig1n, c = c2), heatmap(Fig1o, c = c3),
    heatmap(Fig1p, c = c4), heatmap(Fig1q),         heatmap(Fig1r, c = c4), heatmap(Fig1s, c = c4), heatmap(Fig1t, c = c3),
    layout = (4,5), size = (1600, 1270)
)

savefig("./figures/figure1.png", )
\end{verbatim}

\hypertarget{benchmark-comparison-to-nlmpy-and-nlmr}{%
\section{\texorpdfstring{Benchmark comparison to \texttt{nlmpy} and
\texttt{NLMR}}{Benchmark comparison to nlmpy and NLMR}}\label{benchmark-comparison-to-nlmpy-and-nlmr}}

@@

We implement methods for generating change that are temporally
autocorrelated, spatially autocorrelated, or both.

\(M_t = f(M_{t-1})\)
